Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
missing sentence

\smallskip
\item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P=\sum_{1\leq i\leq k}\alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1,\dots,\alpha_k$ whose coefficients are the mixed volumes of $Q_1,\dots, Q_k$~\cite{ArdilaBenedettiDoker,McMullen-Valuations}. These encode rich combinatorial information when representing generalized permuahedra as positive Minkowski sum of coordinate simplices or hypersimplices~\cite{Postnikov}, and in particular for matroid polytopes~\cite{ArdilaBenedettiDoker}. It would be interesting to get such volume formulas for polytopal realizations of $\b{g}$-vector fans of cluster algebras, and combinatorial interpretations for their coefficients.
\end{itemize}

@@

In other words, extremal adjacent pairs define the extremal rays of the polar of the closed type cone~$\ctypeCone(\Fan)$.
Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.
For instance in 
\arnau{unfinished sentence}

>>>>

\smallskip
\item Once we get a representation of a polytope~$P$ as a signed Minkowski sum~$P = \sum_{i \in [k]}\alpha_i Q_i$, we get a formula for the volume of $P$ as a multivariate polynomial in $\alpha_1,\dots,\alpha_k$ whose coefficients are the mixed volumes of $Q_1,\dots, Q_k$~\cite{ArdilaBenedettiDoker,McMullen-Valuations}. These encode rich combinatorial information when representing generalized permuahedra as positive Minkowski sum of coordinate simplices or hypersimplices~\cite{Postnikov}, and in particular for matroid polytopes~\cite{ArdilaBenedettiDoker}. It would be interesting to get such volume formulas for polytopal realizations of $\b{g}$-vector fans of cluster algebras and gentle algebras, and combinatorial interpretations for their coefficients.
\end{itemize}

@@

In other words, extremal adjacent pairs define the extremal rays of the polar of the closed type cone~$\ctypeCone(\Fan)$.
Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.
For instance, for the $2$-dimensional fan of \cref{exm:typeCone}, the extremal adjacent pairs are~$\{a,b\}$, $\{b,c\}$ and~$\{c,d\}$.
